flowers-pilot-analysis

### 2021-08-18 code/aa-flowers-pilot_analysis.Rmd
move previous game data into data/version_0 and version preprocessing code

Are they getting better over games?
```{r}
d.by_round_metrics %>% left_join(d.games %>% 
                                   select(gameId, condition, chatEnabled))%>%
  mutate(blockName = paste0("Block ", blockNum))%>% 
  ggplot(aes(x = groupNumWords, y = roundPointsAdjusted, 
             color = condition)) + 
  geom_point(alpha = .25) + theme_jmank() + scale_color_bay() + facet_wrap(~blockName) +
  labs(title = "Number of points per trial")
```

>>>>

Are they getting better over games?
```{r}
d.by_round_metrics %>% left_join(d.games %>% 
                                   select(gameId, condition, chatEnabled))%>%
  mutate(blockName = paste0("Block ", blockNum))%>% 
  ggplot(aes(x = log(groupNumWords+1), y = roundPointsAdjusted, 
             color = condition)) + 
  geom_point(alpha = .25) + theme_jmank() + scale_color_bay() + facet_wrap(~blockName) +
  labs(title = "Number of points per trial")
```

### Selecting Hidden Flowers?

```{r}
d.rounds.final %>% left_join(d.games %>% 
                                   select(gameId, condition, chatEnabled)) %>%
  left_join(d.contexts %>% select(gameId, blockNum, trialNum, repNum, playerResponse = label, blinded)) %>%
  mutate(select_blinded = playerId == blinded) %>% 
  group_by(gameId, blockNum, trialNum, repNum, chatEnabled, condition) %>%
  summarize(numSelectHidden = sum(select_blinded)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(condition != "coopCartel") %>%
  ggplot(aes(x = repNum, y = numSelectHidden, color = condition, linetype = languageCondition)) + 
  geom_point(alpha = .1) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name), rows = vars(languageCondition)) + labs(x = "Trial Number", y = "N. Select Hidden")+ scale_color_bay() + theme_jmank()
```
